Searching 21-cm Absorption Systems in Chinese Radio Telescopes

### 2016-11-20 ms_21cm.tex
section Tianlai

\authorrunning{Yu et al.}
\titlerunning{Searching 21-cm absorption systems}

@@

One-month-scan ($n_{\rm obs}=30$) around celestial equator by FAST will have
$N_R\simeq 10^4$ sources whose $F\gtrsim 0.11\ {\rm Jy}$ on 1.4 GHz.
We further assume the independency between $n_R(F)$, $n_R(z)$
and $n_{\rm\HI}(z)$, from $n_{\rm system}(z)$ by integrating
equation (\ref{eq.n_system}), there will be $N_{\rm system}\simeq 90$ absorption
systems found in redshift range $0<z<0.2$.

@@

Tianlai is currently $30\times 12 {\rm m}$ area with
${\rm SEFD}\simeq 300\ {\rm Jy}$. Different from FAST, however,
Tianlai scans all sources in the northern hemisphere of the sky
everyday, and one needs longer periods integration to
identify absorbers with fainter background sources.
We forecast its one-year-survey ability of searching 21-cm
absorption systems in the northern hemisphere.

Because Tianlai locates at latitude
$\phi_{\rm site}=+44^\circ$ and its cylinders are fixed, only
objects at the zenith ($\delta=\phi_{\rm cite}=44^\circ$) fully utilize
the SEFD. On the other hand, higher declination objects
have longer integration time per day. Thus, $\Delta F$ is
a function of $\delta$.

Different declinations have different SEFD.

Result: 80 per year.

>>>>

\authorrunning{Yu et al.}
\titlerunning{Searching 21-cm Absorption Systems}

@@

One-month-scan ($n_{\rm obs}=30$) around celestial equator by FAST will have
$N_R\simeq 10^4$ sources whose $F\gtrsim 0.11\ {\rm Jy}$ on 1.4 GHz.
We further assume the independency between $n_R(F)$, $n_R(z)$
and $n_{\rm\HI}(z)$, from $n_{\rm system}(z)$ by integrating
equation (\ref{eq.n_system}), there will be $N_{\rm system}\simeq 90 {\rm /month}$ absorption
systems found in redshift range $0<z<0.2$.

@@

Tianlai is currently $30\times 12\ {\rm m}$ area with
${\rm SEFD}\simeq 300\ {\rm Jy}$. Different from FAST, however,
Tianlai scans all sources in the northern hemisphere of the sky
everyday, and one needs longer periods integration to
identify absorbers with fainter background sources.
We forecast its one-year-survey ability of searching 21-cm
absorption systems in the northern hemisphere.

Because Tianlai locates at latitude
$\phi_{\rm site}=+44^\circ$ and its cylinders are fixed, only
objects at the zenith ($\delta=\phi_{\rm cite}=44^\circ$) fully utilize
the SEFD. On the other hand, higher declination objects
have longer integration time per day. Thus, $\Delta F$ is
a function of $\delta$, 
\begin{equation}\label{eq.delta_F_delta}
    \Delta F(\delta) = \frac{\rm SEFD}{\cos(\delta-\phi_{\rm site})}
    {\sqrt{\frac{\cos\delta}{n_{\rm pol}\Delta\nu\Delta t(\delta=0)}}},
\end{equation}
where $\Delta t(\delta=0)\simeq 1.17\times 10^5\ {\rm sec}$ is the
total integration time (1-year survey) for objects on celestial equator,
for Tianlai frequency range 800 to 900 MHz ($0.58<z<0.78$).
The effective $N_R$ is given by
\begin{equation}\label{eq.N_R_eff}
    N_R=\int_0^{\pi/2}2\pi\cos\delta
    \left(\int_{10\Delta F(\delta)/r}^{+\infty}
    n_R(F')\diff F'\right)
    \diff\delta.
\end{equation}
Note that the inner flux integration converges as
$F'\rightarrow+\infty$ because $n_R(F)\sim F^{-2.5}$.
Additionally, even if $\tau=\lambda_{\rm obs}/2\pi D\cos\delta$
fails at $\delta\rightarrow\pi/2$ (the north pole
$\tau(\delta=\pi/2)=1$ is always in FoV),
the outer declination integration also converges
as $\delta\rightarrow\pi/2$, because the pole area is
tiny and neglectable.
Equation (\ref{eq.N_R_eff}) gives $N_R\simeq 1.3\times 10^4$,
and applying it to equation (\ref{eq.n_system}) again
we get $N_{\rm system}\simeq 80 {\rm /year}$ absorption
systems found in redshift range $0.58<z<0.78$.
